Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-20 paper/paper.tex
Correct typos #56

\paragraph{Abkhazia and South Ossetia in Georgia}
%Abkhazia
Abkhazia is a western region of Georgia. Abkhazians speak a language unrelated to its parent country's main language, Georgian. 
During the Soviet era, Abkhazia received an enormous influx of Georgians: the 1989 census showed that Abkhazians accounted for only 18\% of the population (Minority At Risk 2006a).
Fearing the disappearance of themselves as an ethnic group, Abkhazians attempted to secede from Georgia and to join Russia in 1957, 1967, and 1978, but the Soviet authority in Moscow rejected these requests (Hewitt 1993, Lakoba 1995).

@@

%Georgian nationalism
Since the late 1980s, however, a nationalist movement led by Zviad Gamsakhurdia, whose party and its coalition partners defeated the Communist Party in the multiparty elections in 1990, instigated ethnic conflict with Ossetians and intensified it with Abkhazians.
The government of Georgia made the Georgian language as the sole official language of the country and banned regional parties from national elections (Minorities At Risk 2006c).
These policies drove Abkhazia and South Ossetia to pursue their secession from Georgia.

@@

\section{Data}\label{data}
This section describes the datasets we use to recover economic growth rates in the four unrecognized states from satellite images of nighttime light.
\subsection{Real GDP}
We use the Penn World Table 9.0 (Freenstra et al.\ 2015) as the data source for real GDP. 
Expenditure-side real GDP at chained PPPs in 2011 US dollars (the variable \textit{rgdpe}) is used because the variable is meant for comparing ``living standards across countries and across years'' (Freenstra et al.\ 2015, Table 1).

@@

\bibitem{} O'Loughlin, John, Gerard Toal, and Rebecca Chamberlain?Creanga. 2013. ``Divided Space, Divided Attitudes? Comparing the Republics of Moldova and Pridnestrovie (Transnistria) Using Simultaneous Surveys.'' \textit{Eurasian Geography and Economics}, 54(2): 227--258.

>>>>

\paragraph{Abkhazia and South Ossetia in Georgia}
%Abkhazia
Abkhazia is a western region of Georgia. Abkhazians speak a language unrelated to its parent country's main language, Georgian. 
During the Soviet era, Abkhazia received an enormous influx of Georgians: the 1989 census showed that Abkhazians accounted for only 18\% of the population (Minorities At Risk 2006a).
Fearing the disappearance of themselves as an ethnic group, Abkhazians attempted to secede from Georgia and to join Russia in 1957, 1967, and 1978, but the Soviet authority in Moscow rejected these requests (Hewitt 1993, Lakoba 1995).

@@

%Georgian nationalism
Since the late 1980s, however, a nationalist movement led by Zviad Gamsakhurdia, whose party and its coalition partners defeated the Communist Party in the multiparty elections in 1990, instigated ethnic conflict with Ossetians and intensified it with Abkhazians.
The government of Georgia made the Georgian language as the sole official language of the country and banned regional parties from national elections (Minorities At Risk 2006b).
These policies drove Abkhazia and South Ossetia to pursue their secession from Georgia.

@@

\section{Data}\label{data}
This section describes the datasets we use to recover economic growth rates in the four unrecognized states from satellite images of nighttime light.
\subsection{Real GDP}
We use the Penn World Table 9.0 (Feenstra et al.\ 2015) as the data source for real GDP. 
Expenditure-side real GDP at chained PPPs in 2011 US dollars (the variable \textit{rgdpe}) is used because the variable is meant for comparing ``living standards across countries and across years'' (Feenstra et al.\ 2015:\ Table 1).

@@

\bibitem{} O'Loughlin, John, Gerard Toal, and Rebecca Chamberlain-Creanga. 2013. ``Divided Space, Divided Attitudes? Comparing the Republics of Moldova and Pridnestrovie (Transnistria) Using Simultaneous Surveys.'' \textit{Eurasian Geography and Economics}, 54(2): 227--258.
